---
title: "Sinusoidal Analysis"
author: "Baidurya Bhattacharyya"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r preloading, include=FALSE}
source('0-libraries.R')
source('1-sinudist.R')
source('2.0-losses.R')
source('2.1-fit.fg.loss.R')
source('2.9-curve.fg.R')
```

## Properties

### Parameters' Effect on Shape of Density
```{r cache=T}
curve(dsinu(x, 0,1,1,1), col='black', xlim=c(0,2), ylim=c(0,2), ylab='Density')
curve(dsinu(x, 1,1,1,1), col='brown', add=T)
curve(dsinu(x, 0,2,1,1), col='blue', add=T)
curve(dsinu(x, 0,1,0.5,1), col='orange', add=T)
curve(dsinu(x, 0,1,2,1), col='red', add=T)
curve(dsinu(x, 0,1,1,2), col='green', add=T)
legend('topright', legend=c('Sinu(0,1)','Sinu(1,1)','Sinu(0,2)','Sinu(0,1,0.5,1)','Sinu(0,1,2,1)','Sinu(0,1,1,2)'), lwd=2, col=c('black','brown','blue','orange','red','green'))
```

### Skewness-Kurtosis Parameters s, k

#### Effect on Shape of Density
```{r}
par(mfcol=c(6,6), cex=0.8, cex.axis=0.5)

omega.vec = c(0.2, 0.6, 1,2,3,4)
chi.vec = c(4,3,2,1, 0.6, 0.2)

for (omega.val in omega.vec) {
  for (chi.val in chi.vec) {
    par(mar=c(0,0,1,0))
    mainlab = paste(omega.val,chi.val, sep=', ')
    curve(dsinu(x, 0,1, omega.val, chi.val), ylim=c(0,6), xaxt='n', yaxt='n', main= mainlab)
  }
}
```



#### s, k jointly affect both Skewness and Kurtosis
```{r}
sinu.kurt.sk = Vectorize(function(s, k) sinu.kurt(s=s, k=k), vectorize.args=c('k','s'))
sinu.skew.sk = Vectorize(function(s, k) sinu.skew(s=s, k=k), vectorize.args=c('k','s'))
```

**Skewness vs s over k-blocks**
```{r, cache=T}
k.vec=c(1:4/4, 1:20/2)
n=length(k.vec)
curve(0*x, xlim=c(0,10), ylim=c(-1.3,2.5), xlab=expression(s), ylab='skewness')
i=0
for (k in k.vec){
  i=i+1
  curve(sinu.skew.sk(k=k, s=x), col=rgb((n-i)/n, i/n, 0), add=T)
}
i.vec=1:n
legend('topright', legend=paste0(s.vec), fill=rgb((n-i.vec)/n, i.vec/n, 0), title=expression(k))
```


**Kurtosis vs k over s-blocks**
```{r, cache=T}
s.vec=c(1:4/4, 1:20/2)
n=length(s.vec)
par(mar = c(4,4,0,0))

curve(0*x, xlim=c(0,20), ylim=c(-1.3,1.9), xlab=expression(k), ylab='kurtosis')
i=0
for (s in s.vec){
  i=i+1
  curve(sinu.kurt.sk(s=s, k=x), col=rgb((n-i)/n, i/n, 0), add=T)
}
i.vec=1:n
legend('topright', legend=paste0(s.vec), fill=rgb((n-i.vec)/n, i.vec/n, 0), title='s')
```

#### Skewness-Kurtosis Coverage by varying s, k
Cache sink for (skew, kurt) based on (s,k)
```{r}

```


```{r coverage, eval=FALSE, include=FALSE, cache=T}
# --- 0. Set Batch Size ---
batch_size <- 500

# --- 1. Data Preparation ---
s.vec <- seq(0,4,by=0.01)
k.vec <- seq(0,6,by=0.01)
s.unique <- unique(s.vec)
k.unique <- unique(k.vec)
n_s <- length(s.unique)
n_k <- length(k.unique)

param.grid <- expand.grid(s = s.unique, k = k.unique)

n_rows <- nrow(param.grid)
n_batches <- ceiling(n_rows / batch_size)

# --- 2. Set up Plot Layout ---
layout(matrix(c(1, 2), 1, 2), widths=c(4, 1))

# --- 3. Create the Main Plot (Empty) ---
par(mar=c(4, 2, 0.5, 0.1)) # Remove right margin
par(cex=0.7)

plot(NULL,
     xlim = c(-1, 2), 
     ylim = c(-1, 4),
     xlab = "skew",
     ylab = "kurt"
)
abline(h=0, v=0, lwd=2)

# --- 4. Loop, Calculate, and Plot in Batches ---
for (i in 1:n_batches) {
  start_index <- (i - 1) * batch_size + 1
  end_index <- min(i * batch_size, n_rows)
  
  batch_data <- param.grid[start_index:end_index, ]
  
  batch_skew <- mapply(sinu.skew, s=batch_data$s, k=batch_data$k, 
                       MoreArgs=list(a=0, d=1, flip=FALSE, cache=TRUE))
  
  batch_kurt <- mapply(sinu.kurt, s=batch_data$s, k=batch_data$k,
                       MoreArgs=list(a=0, d=1, flip=FALSE, cache=TRUE))
  
  # Calculate colors: Red for s, Green for k
  s_norm <- (batch_data$s - min(s.unique)) / (max(s.unique) - min(s.unique))
  k_norm <- (batch_data$k - min(k.unique)) / (max(k.unique) - min(k.unique))
  batch_color <- rgb(s_norm, k_norm, 0)
  
  points(batch_skew, batch_kurt, col = batch_color, pch = 15, cex = 0.8)
  
  # Sys.sleep(0.1)
}

# --- 5. Create the 2D Legend Plot (Once at the end) ---
par(mar=c(5, 0.1, 4, 3)) # Remove left margin
z.index.matrix <- matrix(1:(n_s * n_k), nrow=n_s, ncol=n_k)

# Color vector: Red for s, Green for k
color.vector <- rgb(
  (rep(s.unique, n_k) - min(s.unique)) / (max(s.unique) - min(s.unique)),
  (rep(k.unique, each=n_s) - min(k.unique)) / (max(k.unique) - min(k.unique)),
  0
)

image(s.unique, k.unique, z.index.matrix,
      col = color.vector,
      xlab = "s",
      ylab = "k",
      yaxt = "n")
axis(4)

# Reset layout
par(mfrow=c(1,1), mar=c(5, 4, 4, 2) + 0.1, cex=1.0)
```


## Fitting

### PDF on PDF

#### Helinger

Fitting $N(0,1)$
```{r}
fit1 = fit.fg.Hel(f_family=family_sinu, g=function(x) dnorm(x))
curve.fg(function(x) f_sinu(x, pars=fit1$par), dnorm, xlim=c(-3,3))
```

Fitting LSBeta on $N(0,1)$.
```{r}
fit2 = fit.fg.Hel(family_lsbeta, dnorm)
fit2
curve.fg(function(x) f_lsbeta(x, fit2$par), dnorm, xlim=c(-3,3))
```

Fitting Sinu on $Exp(1)$
```{r}
fit3 = fit.fg.Hel(family_sinu, dexp, support_g=c(0,Inf))
fit3
curve.fg(function(x) f_sinu(x, fit3$par), dexp, xlim=c(0,10))
```

Fitting Beta on $Exp(1)$
```{r}
fit4 = fit.fg.Hel(family_lsbeta, dexp, support_g=c(0,Inf))
fit4
curve.fg(function(x) f_lsbeta(x, fit4$par), dexp, xlim=c(0, 10))
```

```{r}
fit.fg.Hel()
```


### MSM on MSM

### CDF on ECDF (Data)
```{r}

```


